First paper - Draft

### 2017-06-02 paper/paper.Rnw
Started building descriptive tables of sample size

<<loading_data-recoding, cache = TRUE>>=
pisa_all <- read_rds("./data/pisa_listcol.Rdata")
pisa_all2 <- pisa_all

@@

<<modeling, cache = T>>=
adapted_year_data <-
    map(pisa_all2$value, ~ {
      if (unique(.x$wave) == "pisa2000") {
        # pisa2000 has a different coding so here I recode 6 to 7 so that in all waves the top edu
        # is 7 and the bottom is 1
        .x <- 
          mutate(.x, new_hisced = as.character(dplyr::recode(as.numeric(high_edu_broad), `6` = 7)))
      } else {
        .x <-
          mutate(.x, new_hisced = as.character(high_edu_broad))
      }
      .x
})

results_math <- test_diff(adapted_year_data, reliability_pisa, "MATH")
results_read <- test_diff(adapted_year_data, reliability_pisa, "READ")
# US is missing for reading
@

>>>>

<<loading_data-recoding>>=
pisa_all <- read_rds("./data/pisa_listcol.Rdata")
pisa_all2 <- pisa_all

@@

<<modeling>>=
# adapted_year_data <-
#     map(pisa_all2$value, ~ {
#       if (unique(.x$wave) == "pisa2000") {
#         # pisa2000 has a different coding so here I recode 6 to 7 so that in all waves the top edu
#         # is 7 and the bottom is 1
#         .x <- 
#           mutate(.x, new_hisced = as.character(dplyr::recode(as.numeric(high_edu_broad), `6` = 7)))
#       } else {
#         .x <-
#           mutate(.x, new_hisced = as.character(high_edu_broad))
#       }
#       .x
# })
# 
# results_math <- test_diff(adapted_year_data, reliability_pisa, "MATH")
# results_read <- test_diff(adapted_year_data, reliability_pisa, "READ")
# US is missing for reading

# Cache is not working properly for the code above, so I just load the saved cached file
load("./paper/cache/modeling_9a0b38d1d53fa243b0242580f0672fa5.RData")

<<>>=
i <- 3
vals <- intersect(unique(adapted_year_data[[1]]$country), unique(adapted_year_data[[2]]$country))

while (i < 7) {
  vals <- intersect(vals, unique(adapted_year_data[[i]]$country))
  i <- i + 1
}

subset_cnts <- map(adapted_year_data, ~ filter(.x, country %in% vals))

cnt_to_bind <-
  map(subset_cnts, function(df) {

      print(unique(df$wave))
      conf <- if (unique(df$wave) == "pisa2015") pisa2015_conf else pisa_conf
      weights_var <- conf$variables$weightFinal

      split_df <- split(df, df$country)

      split_df_two <-
        map(split_df, ~ {
      # In some countries the quan can't be estimated because of very few obs.
      # The function doesn't stop but returns two NA's.
      quan <- quantile_missing(.x, weights_var)

      # It's very important to create a variable that returns the number of observations of this dummy
      # For each country. Possibly to weight by the number of observations.
      .x$escs_dummy <-
        with(.x, case_when(escs_trend >= quan[2] ~ 1,
                                  escs_trend <= quan[1] ~ 0))
      .x
    })
  unsplit_df <- split_df_two %>% enframe() %>% unnest(value)
  unsplit_df
})

selected_cnt <- map(cnt_to_bind, ~ select(.x, country, high_edu_broad, new_hisced, escs_dummy))

full_cnt <- 
  selected_cnt %>%
  enframe() %>%
  unnest(value) %>%
  mutate(year = as.character(dplyr::recode(.$name,
                `1` = 2000,
                `2` = 2003,
                `3` = 2006,
                `4` = 2009,
                `5` = 2012,
                `6` = 2015)),
         escs_dummy = as.character(escs_dummy))

sample_size <-
  full_cnt %>%
  count(year, country)

high_low_sample <-
  full_cnt %>%
  count(year, country, new_hisced) %>%
  filter(new_hisced %in% c(1, 7)) %>%
  spread(new_hisced, n) %>%
  rename(low_isced = `1`, high_isced = `7`)

ses_sample <-
  full_cnt %>%
  count(year, country, new_hisced, escs_dummy) %>%
  filter(new_hisced == 7 & escs_dummy != 0 | new_hisced == 1 & escs_dummy != 1) %>%
  ungroup() %>%
  select(-new_hisced) %>%
  spread(escs_dummy, n) %>%
  rename(low_low_isced = `0`, high__high_isced = `1`)

left_join(sample_size, high_low_sample) %>%
  left_join(ses_sample)

<<eval = F>>=
# In this chunk you can join reading and math datasets
descrip_math <- map(results_math, ~ rename(.x, mean_math = Mean, se_math = s.e.))
descrip_read <- map(results_read, ~ rename(.x, mean_read = Mean, se_read = s.e.))

map2(results_math, results_read, inner_join, by = "country")
@
